On a Alfvenicity of solar wind discontinuities

### 2024-09-30 article.qmd
Update multi-fluid model for force-free current sheet equilibria

The governing equations for the multi-fluid plasma model can be expressed in conservation law form as follows:

@@

$$
m_α n_α (\frac{∂}{∂ t} + \mathbf{u}_{α} · ∇) \mathbf{u}_α  = - ∇ · \mathbf{P}_α + q_α n_α \left( \mathbf{E} + \frac{\mathbf{u}_α \times \mathbf{B}}{c} \right) + \mathbf{R}_α
$$

where $α$ indicates the particle species, $n_α$ the number density, $m_α$ the mass, $q_α$ the charge, $\mathbf{u}_α$ the bulk velocity, $\mathbf{P}_α$ the pressure tensor, $\mathbf{E}$ the electric field, $\mathbf{B}$ the magnetic induction (magnetic field), and $R_α$ the friction forces.

In this study, we focus on the equilibrium solutions of the set of equations, which implies that the partial derivatives with respect to time are set to zero ($\frac{∂}{∂ t}=0$). 
Our primary interest lies in the current sheet, and we simplify the problem by assuming that the magnetic field depends only on a single Cartesian coordinate, designated as $z$.
Additionally, we assume that the background electron is massless, meaning the electrons follow the magnetic field lines $\mathbf{u}_e \times \mathbf{B} = 0$. 
For further simplification, we also assume the ion populations are gyrotropic, eliminating any non-diagonal terms in the pressure tensor.

Following @steinhauerMultifluidModelOnedimensional2008, we consider a one-dimensional force-free current sheet where $B_x^2 + B_y^2 = B_0^2 = \text{const}$, with all variables dependent solely on $z$. The system comprises multiple steady-state ion species (fluid groups) and a background electron fluid.

Electron motion is along the field lines $\vect{u_e} = Γ_e \vect{B} / (n_e B_z)$. And the conservation of fluid mass $d(n_α u_{αz})/dz = 0$ integrate to a constant parameters $Γ_α = n_α u_{αz}$. The momentum equations for each ion species are given by

>>>>

The governing equations for the multi-fluid collisionless plasma model can be expressed in conservation law form as follows:

@@

$$
m_α n_α (\frac{∂}{∂ t} + \mathbf{u}_{α} · ∇) \mathbf{u}_α  = - ∇ · \mathbf{P}_α + q_α n_α \left( \mathbf{E} + \frac{\mathbf{u}_α \times \mathbf{B}}{c} \right)
$$

where $α$ indicates the particle species, $n_α$ the number density, $m_α$ the mass, $q_α$ the charge, $\mathbf{u}_α$ the bulk velocity, $\mathbf{P}_α$ the pressure tensor, $\mathbf{E}$ the electric field a $\mathbf{B}$ the magnetic induction (magnetic field).

In this study, we focus on the equilibrium solutions of the set of equations, which implies that the partial derivatives with respect to time are set to zero ($\frac{∂}{∂ t}=0$). Since our primary interest lies in the force-free current sheet, we assume that the magnetic field depends only on a single Cartesian coordinate, $z$, leading to the force-free condition $B_x^2 + B_y^2 = B_0^2 = \text{const}$. Additionally, we assume that the background electron is massless, meaning the electrons follow the magnetic field lines $\mathbf{u}_e \times \mathbf{B} = 0$. For further simplification, we also assume the ion populations are gyrotropic, eliminating any non-diagonal terms in the pressure tensor.

Under these assumptions, the conservation of fluid mass, expressed as $d(n_α u_{αz})/dz = 0$, integrates to a constant parameter, $Γ_α = n_α u_{αz}$. The electron motion is aligned with the magnetic field lines, resulting in $\vect{u_e} = Γ_e \vect{B} / (n_e B_z)$. The momentum equations for each ion species are then given by:
